Kernel Smoothing And Heat Equation

### 2020-12-08 latex/draft.tex
fixed boundary issue for circular one, and updated the notes  draft.

\begin{itemize}
% 12/01/2020  
\item 12/01/2020. 
\begin{figure}[H]
\includegraphics[width=\linewidth]{pic/sim.plot1.eps}
\includegraphics[width=\linewidth]{pic/sim.plot2.eps}
\includegraphics[width=\linewidth]{pic/sim.plot3.eps}
\end{figure}

>>>>

\begin{itemize}
  % 12/08/2020  
\item 12/08/2020. 
Fixed the boundary issue for circular situation.

\begin{table}[H]
\centering
\begin{tabular}{l|l| l}
\hline\hline
& (theoretical MSE =$1.96\times 10^{-7}$) & (theoretical MSE =$4.93\times 10^{-9}$)\\
k & empirical MSE  ($\sigma=1$) &empirical MSE  ($\sigma=0.1$) \\\hline 
0.1&0.0020 $(6.65\times 10^{-6})$ & $2.02\times 10^{-5} (7.35\times 10^{-10})$\\
1 & 0.0021 $(9.69\times 10^{-6})$ & $1.95\times 10^{-5}  (7.00\times 10^{-10})$\\
2 & 0.0021 $(8.33\times 10^{-6})$ & $1.95\times 10^{-5} (7.17\times 10^{-10})$\\
2.4 & 0.0024 $(1.22\times 10^{-5})$ & $2.41\times 10^{-5} (1.17\times 10^{-9})$\\
3 & 0.0029 $(1.51\times 10^{-5})$ & $2.82\times 10^{-5} (1.59\times 10^{-9})$\\
4 & 0.0041 $(3.52\times 10^{-5})$ &  $4.36\times 10^{-5} (3.42\times 10^{-9})$\\
5 & 0.0050 $(5.36\times 10^{-5})$ &  $5.07\times 10^{-5} (5.24\times 10^{-9})$\\\hline
\end{tabular}
\caption{1000 times simulation for empirical MSE at extreme point at boundary}
\end{table}

\begin{figure}[H]
\includegraphics[width=\linewidth]{pic/sim.plot10.eps}
\end{figure}
\begin{verbatim}
  Adaptive    logb=-3  logb=-2.4  logb=-1.8  logb=-1.2  logb=-0.6 
0.01650001 1.00313133 1.00313133 0.22355199 0.05497094 0.01329125 
    logb=0   logb=0.6   logb=1.2   logb=1.8   logb=2.4     logb=3 
0.02305490 0.03210026 0.03280336 0.50068896 0.50068896 0.50068896
\end{verbatim}

\begin{figure}[H]
\includegraphics[width=\linewidth]{pic/sim.plot11.eps}
\end{figure}
\begin{verbatim}
    Adaptive      logb=-3    logb=-2.4    logb=-1.8    logb=-1.2    logb=-0.6 
0.0004494958 0.0100313133 0.0100313133 0.0022356024 0.0005502092 0.0005894302 
      logb=0     logb=0.6     logb=1.2     logb=1.8     logb=2.4       logb=3 
0.0197699286 0.0292714857 0.0299909440 0.4990188656 0.4990188656 0.4990188656 
\end{verbatim}

TODOLIST:
\begin{enumerate}
\item 
\item
\end{enumerate}

% 12/01/2020  
\item 12/01/2020. 
\begin{figure}[H]
\includegraphics[width=\linewidth]{pic/sim.plot1.eps}
\includegraphics[width=\linewidth]{pic/sim.plot2.eps}
\includegraphics[width=\linewidth]{pic/sim.plot3.eps}
\end{figure}
